Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-05-10 Grassmannian_cells.tex
Theorem 4.22 (former 4.20) update
Added a remark after the claim

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $I\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^I)$ admits a cell decomposition.
\end{theorem}
\begin{proof}
  We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip

  \noindent{\bf Claim.}
  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition which is compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
  \begin{itemize}
    \item[($\dagger$)] For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
  \end{itemize}
  \vs

>>>>

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition. In particular, every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
\end{theorem}
\begin{proof}

	We work by induction on $m$.
  When $m=1$, the claim is trivial since in this case all quiver Grassmannians are points.
  We establish the result for $m\ge2$ by proving the following more general statement:\bigskip

  \noindent{\bf Claim.}
  For any admissible sequence $\bfI=(I_0,\ldots,I_k)$ with $k<m$ and any subset $J\subset I_0$, the quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition which is compatible with the unique map $\pi_{m+1}^{J,\bfI}:\tilde P_{m+1}^J\to\tilde P_{m+1}^\bfI$ from Lemma~\ref{le:truncated quotients} in the following sense:
  \begin{itemize}
    \item[($\dagger$)] For any $V\in\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ such that $\pi_{m+1}^{J,\bfI}(V)\neq 0$, we have $\pi_{m+1}^{J,\bfI}(V')\neq 0$ for all $V'\in C_V$, where $C_V$ is the affine cell which contains $V$.
  \end{itemize}
  \vs
Note that having proved the claim, for $|J|\leq n-2$ the statement itself is obtained when setting $\bfI=(J\cup\{i\})$ for any $i\in\{1,\ldots,n\}\backslash\{J\}$. For $|J|=n-1$, we can apply Lemma~\ref{le:truncated quotients}, i.e. $P_{m+1}^J\cong\tilde P_{m,j}^{\{j\}}$ with $J^c=\{j\}$, together with the fact that $\tilde P_{m,j}^{\{j\}}$ is obtained when translating $\tilde P_{m}^{\{j\}}$ in the universal covering quiver. Clearly, translation does not affect quiver Grassmannians when also translating dimension vectors $\tbfe$, i.e. quiver Grassmannians of $\tilde P_{m,j}^{\{j\}}$ are just the same as those of $\tilde P_{m}^{\{j\}}$.

Finally, recall that the preprojective representations $\tilde P_{m+1}$ and their quiver Grassmannians are obtained when setting $J=\varnothing$ and considering any short exact sequence
		$$\ses{\tilde P_{m,j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\{j\}}}$$
for $j\in\{1,\ldots,n\}$. Then we can use the fact that $\tilde P_{m,j}$ is the translation of $\tilde P_m$.
